% Ryan Avery - Curriculum Vitae
% Copyright 2019 Ryan Avery
% Email: ravery@ucsb.edu
% Web: http://caylor.eri.ucsb.edu/people/avery/

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts

% what is your name?
\newcommand{\myname}{Ryan Avery}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{1.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{20}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
	left=1.0in,
	top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
			\setlength{\parskip}{0em}
			\setlength{\itemsep}{\listitemspace}
			\setlength{\parsep}{\listitemspace}}}
	{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
	labelindent=0em,
	topsep=0em,
	partopsep=0em,
	itemsep=\listitemspace,
	parsep=\listitemspace,
	font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\myname},
	pdfkeywords = {ecohydrology, vegetation remote sensing, isotope hydrology, machine learning, groundwater},
	pdftitle = {\myname: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\begin{document}
	\raggedright
	
	% display name as the document title
	\namefont{\myname}
	
	% contact info
	\vspace{1em}
	\begin{minipage}[t]{0.495\textwidth}
		Department of Geography \\
		University of California, Santa Barbara \\
		Santa Barbara, California
	\end{minipage}
	\begin{minipage}[t]{0.495\textwidth}
		Email: ravery@ucsb.edu \\
		Web: \href{http://caylor.eri.ucsb.edu/people/avery/}{http://caylor.eri.ucsb.edu/people/avery/} \\
		Phone: +1 916 897 7076
	\end{minipage}
	\vspace{0.5em}
	
	
	
	\section*{Education}
	
	\begin{tablist}
		
		\item[Ph.D. student] \tab Geography, University of California, Santa Barbara, 2021 (expected) \\
		Adviser: Kelly Caylor 
		
		\item[B.S.]  \tab Environmental Sciences: Biological Sciences Concentration, University of California, Berkeley, 2016
		
	\end{tablist}	


	
	\section*{Research Interests}
	
	\begin{itemize}
		
		\item Ecohydrological measurement and modeling, particularly isotope hydrology and water balance estimation
		
		\item Classification and clustering of multispectral imagery for object detection and segmentation
		
		\item Spatial data science: computational statistics, machine learning, big data, visualization, spatial analysis
		
		\item Coupled human-natural systems and decison making and policy around water resources 
		
	\end{itemize}
	
	
	
	\section*{Publications}
	
	
	\subsection*{Reports and Working Papers}
	
	\begin{tablist}
		
		\item[2017] \tab \enquote{Detecting Changes in Nighttime Sky Brightness over Grand Teton National Park with the Suomi NPP VIIRS Sensor} Avery, R., V. Warda, S. Chu, S. Chao. 2017. NASA DEVELOP Technical Report. 

	    \item[2017] \tab \enquote{Enhancements to Visualization of CALIPSO (VOCAL) through Case Studies of Saharan Dust} Pampalone, C. R. Avery, W. Turner. 2017. NASA DEVELOP Technical Report.

        \item[2017] \tab \enquote{A Threshold-Based Decision Tree Approach to Mapping Landscape Disturbance in Glacier National Park} Avery, R., Mays, C., Alvarado A. 2017. NASA DEVELOP Technical Report.

        \item[2016] \tab \enquote{Mapping Invasive Species to Efficiently Monitor Southwestern National Park Areas} Avery, R., K. Landesman, T. Whaley. 2016. NASA DEVELOP Technical Report.
	
	
    \subsection*{Manuscripts in Preparation}
	
	\begin{tablist}
				
		\item[\the\year] \tab Avery, R., L. Estes, K. Caylor, S., R. Eastman, Ye, L. Song \enquote{A Convolutional Neural Network Approach for Segmenting Smallholder Agriculture and Comparison to Modern Machine Learning Methods} Target: \textit{Remote Sensing of Environment}, Summer 2019.
		
		\item[\the\year] \tab Avery, R., K. Caylor, M. McCabe, M. Mayes, L. Estes \enquote{Field-Scale Evapotranspiration Maps across Global Dryland Center Pivot Agriculture} Target: \textit{Remote Sensing of Environment}, Fall 2019.
		
		\item[\the\year] \tab Tuholske, C., K. Caylor, T. Evans, R. Avery \enquote{Triangulating Urban Agglomerations Hotspots Across Africa} Target: \textit{Environmental Research Letters}, Spring 2019.
	
	\end{tablist}
	
	\subsection*{Campus Talks}
	
    \section*{Conference Activity}
	
	
	\subsection*{Conference Presentations}
	
	Presenting author \textit{italicized}, if other.\bigskip
	
	\begin{tablist}
		
		\item[2019] \tab Boeing, G. \enquote{The Evolution of American Street Network Design and Planning.} Urban Affairs Association Annual Conference. Los Angeles, California. Apr 24--27.
		
		\item[2019] \tab Abdelkader, A., G. Boeing, \textit{B.~T. Fasy}, D.~L. Millman. \enquote{Local Persistent Homology-Based Distances between Nonplanar Road Networks.} Joint Mathematics Meetings. Baltimore, Maryland. Jan 16--19.
		
		\item[2019] \tab Boeing, G. \enquote{Street Network Patterns, Orientation, and Entropy around the World.} Transportation Research Board Annual Meeting. Washington, DC. Jan 13--17.
		
		\item[2018] \tab \textit{Abdelkader, A.}, G. Boeing, B.~T. Fasy, D.~L. Millman. \enquote{Topological Distance Between Nonplanar Transportation Networks.} Fall Workshop on Computational Geometry. Queens, New York. Oct 26--27.
		
		\item[2018] \tab Boeing, G. \enquote{Sociodemographic Representation of Online Rental Housing Listings: Information Surpluses and Deficits.} Association of Collegiate Schools of Planning Annual Conference. Buffalo, New York. Oct 25--28.
		
		\item[2018] \tab \textit{Waddell, P.}, I. Garcia-Dorado, S. Maurer, G. Boeing, M. Gardner, E. Porter, D. Aliaga. \enquote{Urban Modeling Without Zones: A Metropolitan Graph-Based Microsimulation of Real Estate Markets and Transportation.} Association of Collegiate Schools of Planning Annual Conference. Buffalo, New York. Oct 25--28.
				
	\end{tablist}
	
	
	
	\section*{Grants and Awards}
	
	\subsection*{Grants and Fellowships}
	
	\begin{tablist}
		
		\item[2018] \tab National Geographic and Microsoft AI for Earth research grant (\$100,000). Role: Primary Author and Project Member.
				
	\end{tablist}
	
	
	
	\section*{Teaching Experience}
	
	\subsection*{University of California, Santa Barbara}
	
	\begin{itemize}
		
		\item Big Data for Cities (Spring '19)
		
		\item Advanced Spatial Analysis of Urban Systems (Spring '19)
		
		\item Urban Theory and Science (Fall '18)
		
	\end{itemize}
	
	\subsection*{University of California, Berkeley}
	
	\begin{itemize}
		
		\item Urban Informatics and Visualization (Fall '13, '14, '15, '16: grad student instructor, co-lead instructor)
		
	\end{itemize}
	
	\subsection*{Planetizen}
	
	\begin{itemize}
		
		\item Python for Planners; Data Analysis and Visualization for Planners; Geospatial Data Analysis; Street Network Analysis
		
	\end{itemize}
	
	
	\section*{Service}
	
	\subsection*{Peer Reviewer}
	
	\begin{itemize}
		
		\item \textit{Cities}
		
		\item \textit{Environment and Planning B: Urban Analytics and City Science}
		
		\item \textit{European Physical Journal: Data Science}
		
		\item \textit{International Journal of Geographical Information Science}
		
		\item \textit{International Planning Studies}

		\item \textit{International Regional Science Review}
		
		\item \textit{ISPRS International Journal of Geo-Information}
		
		\item \textit{Journal of the American Planning Association}
		
		\item \textit{Journal of Transport and Land Use}
		
		\item \textit{Landscape and Urban Planning}
		
		\item \textit{Mathematics}
		
		\item \textit{Nonlinear Dynamics}
		
		\item \textit{PLOS One}
		
		\item \textit{Sustainable Cities and Society}
		
		\item \textit{Transactions in GIS}
		
		\item \textit{Urban Design International}
		
	\end{itemize}
	
	\subsection*{Service to Field}
	
	\begin{itemize}
		
		\item Review and Appraisal Committee, Association of Collegiate Schools of Planning, 2018--
		
		\item Scientific Committee, Symposium on Simulation for Architecture and Urban Design, 2018--
		
		\item Book review editor, \textit{Berkeley Planning Journal}, 2013--14
		
	\end{itemize}
	
	\subsection*{Service to Department}
	
	\begin{itemize}
		
		\item Standing Committee on Digital Proficiencies and Quantitative Methods, NU CSSH, 2018--
		
		\item Ph.D. program faculty representative, UC Berkeley DCRP, 2015--16
		
		\item Ph.D. program admissions committee, UC Berkeley DCRP, 2015--16
		
	\end{itemize}
	
	
	
	\section*{Professional Affiliations}
	
	\begin{itemize}
		
		\item American Association of Geographers
		
		\item American Planning Association
		
		\item Association of Collegiate Schools of Planning
		
		\item Association for Computing Machinery
		
		\item Complex Systems Society
		
		\item Regional Studies Association
		
		\item New York Academy of Sciences
		
		\item Project Management Institute
		
		\item Python Software Foundation
		
		\item Urban Affairs Association	
		
	\end{itemize}
	
	
	
	\section*{Credentials}
	
	\begin{itemize}
		
		\item U.S. Department of Defense secret clearance
		
		\item U.S. Department of Homeland Security public trust
		
		\item Project Management Professional (PMP)
		
	\end{itemize}
	
	
	
	\section*{Consulting Engagements}
	
	\begin{tablist}
		
		\item[2017--19] \tab The Public Good Projects	
		
		\item[2017--18] \tab Calthorpe Analytics
		
		\item[2016--18] \tab UrbanSim Inc.
		
		\item[2013--18] \tab Avalon Health Economics
		
		\item[2013]     \tab Raimi \& Associates
		
		\item[2009--13] \tab Accenture
		
	\end{tablist}
	
	
	
	\section*{Professional Experience}
	
	\begin{tablist}
		
		\item[2009--13] \tab Accenture, Consultant/Project Manager. London, England; New York, New York; San Diego, California.
		
		\item[2007--09] \tab Permission Data, Front-End Systems Product Manager. New York, New York.
		
		\item[2004--07] \tab Acumen Inc., Web Systems Developer. Mesa, Arizona.
		
	\end{tablist}
	
	
	
	\section*{Selected Media Coverage}
	
	Complete listing available at https://geoffboeing.com/press/ \bigskip
	
	\begin{tablist}
		
		\item 2018 \tab \textit{CityLab}. \enquote{Visualizing the Hidden Logic of Cities} Jul 26.
		
		\item 2018 \tab \textit{New Statesman CityMetric}. \enquote{Do British Cities Have Grid Systems? We Used Science to Find Out.} Jul 23.
		
		\item 2018 \tab \textit{99 Percent Invisible}. \enquote{On the Grid: Visualizing Street Network Orientations Across 50 Global Cities.} Jul 20.
		
		\item 2018 \tab \textit{Fast Company}. \enquote{How Crazy Is Your City's Plan?} Jul 16.
		
		\item 2018 \tab \textit{The Boston Globe}. \enquote{Boston's Streets Do Go in All Sorts of Directions.} Jul 12.
		
		\item 2018 \tab \textit{Slate}. \enquote{Elegant Graphs Reduce 25 American Cities to Their Design Essence.} Jul 11.	
		
		\item 2018 \tab \textit{Chicago Magazine}. \enquote{What Craigslist Can Tell Us About Rents in Chicago.} Jan 24.
		
		\item 2017 \tab \textit{The San Francisco Chronicle}. \enquote{Stunning, Simple Maps Show San Francisco versus Other Global Cities.} Jun 19.
		
		\item 2017 \tab \textit{The Daily Mail}. \enquote{Square Mile Maps Reveal How Different the World's Cities Really Are.} Jun 9.
		
		\item 2017 \tab \textit{Forbes}. \enquote{Understanding Our Cities, Thanks to Beautiful Maps.} Feb 7.
		
		\item 2017 \tab \textit{Fast Company}. \enquote{Turn Your Local Streets into a Map That Reveals the Character of Your Neighborhood.} Feb 6.
		
		\item 2017 \tab \textit{Domus Magazine}. \enquote{Do-It-Yourself City Mapping.} Jan 23.
		
		\item 2017 \tab \textit{CityLab}. \enquote{A Digital Window into Your City's Urban Form.} Jan 17.
		
		\item 2017 \tab \textit{Discovery News}. \enquote{Compare City Street Grids One Square Mile at a Time.} Jan 9.
		
		\item 2016 \tab \textit{The Washington Post}. \enquote{What More Than 1 Million Craigslist Rental Listings Tell Us about the Housing Market.} Sep 1.
		
		\item 2016 \tab \textit{Fast Company}. \enquote{11 Million Craigslist Ads Show Which Cities Have the Highest Rents.} Sep 1.
		
		\item 2016 \tab \textit{NextCity}. \enquote{What 11 Million Craigslist Posts Show About Affordable Housing.} Aug 26.
		
	\end{tablist}
	
	
	
	\section*{Skills and Methods}
	
	\subsection*{Statistical and Computational Methods}
	
	\begin{itemize}
		
		\item Computational statistics and machine learning, systems analysis, data mining, data wrangling, Python (including numpy, scipy, pandas, matplotlib, statsmodels, networkx, and scikit-learn), JavaScript, HTML, web scraping, MySQL, Postgres, and various other databases.
		
	\end{itemize}
	
	\subsection*{Geospatial Methods}
	
	\begin{itemize}
		
		\item Spatial analysis, network analysis, PostGIS, QGIS, ArcGIS, geopandas, Leaflet, CARTO, agent-based spatial modeling and microsimulation. I developed and maintain the OSMnx street network modeling software.
		
	\end{itemize}
	
	\subsection*{International Experience}
	
	\begin{itemize}
		
		\item I have previously worked professionally in the United States, the United Kingdom, Malawi, Mozambique, and Cambodia.
		
	\end{itemize}
	
	
	
	% display today's date as Month Year after a vertical space below the end of the text
	\begin{center}
		\vspace{6em}
		%\vfill
		Updated \monthyeardate\today
	\end{center}
	
	
	
\end{document}
